Transforming Partially Ordered HTN Problems to Totally Ordered

### 2022-11-21 paper/paper-mainfile.tex
adjust table size

\section{Linearization Procedure}
The basic linearization process consists of inferring preconditions and effects for compound tasks, inferring additional orderings to the sub-tasks based on the preconditions and effects (inferred or \enquote{real} in the case of primitive tasks) of method sub-tasks, and adding them only if they do not conflict with the originally required orderings.

@@

\subsection{Linearization Using Inferred Preconditions and Effects}

\begin{algorithm}
	\caption{Linearization using inferred set of preconditions and effects} %\caption{Calculation of linearized methods}
	\label{alg:Algorithm1}	
	\KwData{$(F, T_P, T_C, \delta, M)$}
	\KwResult{$(F, T_P, T_C, \delta, M)$}

@@

\begin{table}[h]
	\scalebox{0.64} {
		\begin{tabular}{lccccccccccccccccccccccccl} 
			\toprule 
			&& \multicolumn{2}{c}{  \rotatebox{90}{rc2(Add)}} & 
			\multicolumn{2}{c}{   \rotatebox{90}{rc2(Filter)}} & 
			\multicolumn{2}{c}{  \rotatebox{90}{rc2(FF)}}
			& \multicolumn{2}{c}{   \rotatebox{90}{rc2(LMC)}}  
			& \multicolumn{2}{c}{  \rotatebox{90}{HTN2SAS}}
			& \multicolumn{2}{c}{  \rotatebox{90}{HyperTensioN}}
			& \multicolumn{2}{c}{  \rotatebox{90}{Lilotane}} \\ 
			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}  \cmidrule(lr){13-14} \cmidrule(lr){15-16}    
			& &PO & TO & PO & TO & PO & TO & PO & TO   \\ 
			\midrule 
			Barman-BDI  \\ 
			Monroe Fully Observ. \\ 
			Monroe Part. Observ. \\ 
			PCP\\ 
			Rover  \\ 
			Satellite  \\ 
			Transport \\ 
			UM-Translog \\ 
			Woodworking \\ 
			\midrule 
			Monroe  \\ 
			SmartPhone \\ 
			Zenotravel \\ 
			\midrule 
			Coverage \\ 
			Norm. coverage  \\ 
			\bottomrule
		\end{tabular} 	
	}
\end{table}

\begin{table}[h]
	\scalebox{0.64} {
		\begin{tabular}{lccccccccccccccccccccccccl} 
			\toprule 
			&& \multicolumn{2}{c}{  \rotatebox{90}{rc2(Add)}} & 
			\multicolumn{2}{c}{   \rotatebox{90}{rc2(Filter)}} & 
			\multicolumn{2}{c}{  \rotatebox{90}{rc2(FF)}}
			& \multicolumn{2}{c}{   \rotatebox{90}{rc2(LMC)}} 
			& \multicolumn{2}{c}{  \rotatebox{90}{HTN2SAS}}
			& \multicolumn{2}{c}{  \rotatebox{90}{HyperTensioN}}
			& \multicolumn{2}{c}{  \rotatebox{90}{Lilotane}} \\ 
			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}  \cmidrule(lr){13-14} \cmidrule(lr){15-16}    
			& &PO & TO & PO & TO & PO & TO & PO & TO   \\ 
			\midrule 
			Barman-BDI  \\ 
			Monroe Fully Observ. \\ 
			Monroe Part. Observ. \\ 
			PCP\\ 
			Rover  \\ 
			Satellite  \\ 
			Transport \\ 
			UM-Translog \\ 
			Woodworking \\ 
			\midrule 
			Monroe  \\ 
			SmartPhone \\ 
			Zenotravel \\ 
			\midrule 
			IPC \\
			\bottomrule
		\end{tabular} 	
	}
\end{table}

@@

\begin{table}[h]
	\scalebox{0.64} {
		\begin{tabular}{lccccccccccccccccccccccccl} 
			\toprule 
			&& \multicolumn{2}{c}{  \rotatebox{90}{rc2(Add)}} & 
			\multicolumn{2}{c}{   \rotatebox{90}{rc2(Filter)}} & 
			\multicolumn{2}{c}{  \rotatebox{90}{rc2(FF)}}
			& \multicolumn{2}{c}{   \rotatebox{90}{rc2(LMC)}}  
			& \multicolumn{2}{c}{  \rotatebox{90}{HTN2SAS}}
			& \multicolumn{2}{c}{  \rotatebox{90}{HyperTensioN}}
			& \multicolumn{2}{c}{  \rotatebox{90}{Lilotane}} \\ 
			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}  \cmidrule(lr){13-14} \cmidrule(lr){15-16}    
			& &PO & TO & PO & TO & PO & TO & PO & TO   \\ 
			\midrule 
			Barman-BDI  \\ 
			Monroe Fully Observ. \\ 
			Monroe Part. Observ. \\ 
			PCP\\ 
			Rover  \\ 
			Satellite  \\ 
			Transport \\ 
			UM-Translog \\ 
			Woodworking \\ 
			\midrule 
			Monroe  \\ 
			SmartPhone \\ 
			Zenotravel \\ 
			\midrule 
			Coverage \\ 
			Norm. coverage  \\ 
			\bottomrule
		\end{tabular} 	
	}
\end{table}

\begin{table}[h]
	\scalebox{0.64} {
		\begin{tabular}{lccccccccccccccccccccccccl} 
			\toprule 
			&& \multicolumn{2}{c}{  \rotatebox{90}{rc2(Add)}} & 
			\multicolumn{2}{c}{   \rotatebox{90}{rc2(Filter)}} & 
			\multicolumn{2}{c}{  \rotatebox{90}{rc2(FF)}}
			& \multicolumn{2}{c}{   \rotatebox{90}{rc2(LMC)}}  
			& \multicolumn{2}{c}{  \rotatebox{90}{HTN2SAS}}
& \multicolumn{2}{c}{  \rotatebox{90}{HyperTensioN}}
& \multicolumn{2}{c}{  \rotatebox{90}{Lilotane}} \\ 
			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}  \cmidrule(lr){13-14} \cmidrule(lr){15-16}    
			& &PO & TO & PO & TO & PO & TO & PO & TO   \\ 
			\midrule 
			Barman-BDI  \\ 
			Monroe Fully Observ. \\ 
			Monroe Part. Observ. \\ 
			PCP\\ 
			Rover  \\ 
			Satellite  \\ 
			Transport \\ 
			UM-Translog \\ 
			Woodworking \\ 
			\midrule 
			Monroe  \\ 
			SmartPhone \\ 
			Zenotravel \\ 
			\midrule 
			IPC \\
			\bottomrule
		\end{tabular} 	
	}
\end{table}

>>>>

\section{Inference of Preconditions and Effects}
The basic linearization process consists of inferring preconditions and effects for compound tasks, inferring additional orderings to the sub-tasks based on the preconditions and effects (inferred or \enquote{real} in the case of primitive tasks) of method sub-tasks, and adding them only if they do not conflict with the originally required orderings.

@@

\subsection{Inference of Preconditions and Effects for Lifted Domain}
In a lifted format, tasks and methods accept parameters, referring to any object of a specific type. Thus actions within a method have effects and preconditions that are symmetrical in terms of interactions within the method.

E.g.\ the task \textit{navigate(waypoint1, waypoint2)} will end up with some set of actions  $\bar{a}$ once decomposed. If you replace the passed parameters \textit{waypoint1} with \textit{waypoint3} and \textit{waypoint2} with \textit{waypoint4}, then \textit{navigate(waypoint3, waypoint4)} will have the same set of actions $\bar{a}$. This is true for all possible tasks by simple induction over the decomposition process.

Thus for each method, we can \enquote{ground} it in the standard way, but using an arbitrary object instead of all objects that exist in the domain.

Specifically, let $\sigma$ be the set of parameters for the method. Then for each parameter of the method, the set of typed objects $\omega$ has one object of the corresponding type, and $|\omega| = |\sigma|$. Then $\sigma(a, \omega)$, the groundings of a transition schema $a$ over $\omega$, corresponds to the ground method obtained by substituting $\sigma$ with the corresponding object of correct type taken from $\omega$.

Where a task accepts two parameters of the same type under different names, it is assumed those are different objects. For example, for \textit{Navigate(pt0, pt1, rover)}, \textit{pt0} and \textit{pt1} are assumed as different objects. % This is illustrated in Figure~\ref{CompoundPreEffForLifted}.

This allows actions to have some ground \enquote{predicate} \textit{at\_waypoint1}, rather than $at(?waypoint)$. The resulting \enquote{predicates} can be used to order the sub-tasks, while groundings for methods are discarded. For variant 1, only one linearized lifted method per partially-ordered lifted method is produced.

\section{Linearization Using Inferred Preconditions and Effects}
\begin{algorithm}
	\caption{Linearization using inferred set of preconditions and effects} %\caption{Calculation of linearized methods}
	\label{alg:Algorithm1}	
	\KwData{$(F, T_P, T_C, \delta, M)$}
	\KwResult{$(F, T_P, T_C, \delta, M)$}

@@

\begin{table*}[h]
	\scalebox{1} {
		\begin{tabular}{lccccccccccccccccccccccccl} 
			\toprule 
			&& \multicolumn{2}{c}{  \rotatebox{90}{rc2(Add)}} & 
			\multicolumn{2}{c}{   \rotatebox{90}{rc2(Filter)}} & 
			\multicolumn{2}{c}{  \rotatebox{90}{rc2(FF)}}
			& \multicolumn{2}{c}{   \rotatebox{90}{rc2(LMC)}}  
			& \multicolumn{2}{c}{  \rotatebox{90}{HTN2SAS}}
			& \multicolumn{2}{c}{  \rotatebox{90}{HyperTensioN}}
			& \multicolumn{2}{c}{  \rotatebox{90}{Lilotane}} \\ 
			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}  \cmidrule(lr){13-14} \cmidrule(lr){15-16}    
			& &PO & TO & PO & TO & PO & TO & PO & TO   \\ 
			\midrule 
			Barman-BDI  \\ 
			Monroe Fully Observ. \\ 
			Monroe Part. Observ. \\ 
			PCP\\ 
			Rover  \\ 
			Satellite  \\ 
			Transport \\ 
			UM-Translog \\ 
			Woodworking \\ 
			\midrule 
			Monroe  \\ 
			SmartPhone \\ 
			Zenotravel \\ 
			\midrule 
			Coverage \\ 
			Norm. coverage  \\ 
			\bottomrule
		\end{tabular} 	
	}
\end{table*}

\begin{table*}[h]
	\scalebox{1} {
		\begin{tabular}{lccccccccccccccccccccccccl} 
			\toprule 
			&& \multicolumn{2}{c}{  \rotatebox{90}{rc2(Add)}} & 
			\multicolumn{2}{c}{   \rotatebox{90}{rc2(Filter)}} & 
			\multicolumn{2}{c}{  \rotatebox{90}{rc2(FF)}}
			& \multicolumn{2}{c}{   \rotatebox{90}{rc2(LMC)}} 
			& \multicolumn{2}{c}{  \rotatebox{90}{HTN2SAS}}
			& \multicolumn{2}{c}{  \rotatebox{90}{HyperTensioN}}
			& \multicolumn{2}{c}{  \rotatebox{90}{Lilotane}} \\ 
			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}  \cmidrule(lr){13-14} \cmidrule(lr){15-16}    
			& &PO & TO & PO & TO & PO & TO & PO & TO   \\ 
			\midrule 
			Barman-BDI  \\ 
			Monroe Fully Observ. \\ 
			Monroe Part. Observ. \\ 
			PCP\\ 
			Rover  \\ 
			Satellite  \\ 
			Transport \\ 
			UM-Translog \\ 
			Woodworking \\ 
			\midrule 
			Monroe  \\ 
			SmartPhone \\ 
			Zenotravel \\ 
			\midrule 
			IPC \\
			\bottomrule
		\end{tabular} 	
	}
\end{table*}

@@

\begin{table*}[h]
	\scalebox{1} {
		\begin{tabular}{lccccccccccccccccccccccccl} 
			\toprule 
			&& \multicolumn{2}{c}{  \rotatebox{90}{rc2(Add)}} & 
			\multicolumn{2}{c}{   \rotatebox{90}{rc2(Filter)}} & 
			\multicolumn{2}{c}{  \rotatebox{90}{rc2(FF)}}
			& \multicolumn{2}{c}{   \rotatebox{90}{rc2(LMC)}}  
			& \multicolumn{2}{c}{  \rotatebox{90}{HTN2SAS}}
			& \multicolumn{2}{c}{  \rotatebox{90}{HyperTensioN}}
			& \multicolumn{2}{c}{  \rotatebox{90}{Lilotane}} \\ 
			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}  \cmidrule(lr){13-14} \cmidrule(lr){15-16}    
			& &PO & TO & PO & TO & PO & TO & PO & TO   \\ 
			\midrule 
			Barman-BDI  \\ 
			Monroe Fully Observ. \\ 
			Monroe Part. Observ. \\ 
			PCP\\ 
			Rover  \\ 
			Satellite  \\ 
			Transport \\ 
			UM-Translog \\ 
			Woodworking \\ 
			\midrule 
			Monroe  \\ 
			SmartPhone \\ 
			Zenotravel \\ 
			\midrule 
			Coverage \\ 
			Norm. coverage  \\ 
			\bottomrule
		\end{tabular} 	
	}
\end{table*}

\begin{table*}[h]
	\scalebox{1} {
		\begin{tabular}{lccccccccccccccccccccccccl} 
			\toprule 
			&& \multicolumn{2}{c}{  \rotatebox{80}{rc2(Add)}} & 
			\multicolumn{2}{c}{   \rotatebox{80}{rc2(Filter)}} & 
			\multicolumn{2}{c}{  \rotatebox{80}{rc2(FF)}}
			& \multicolumn{2}{c}{   \rotatebox{80}{rc2(LMC)}}  
			& \multicolumn{2}{c}{  \rotatebox{80}{HTN2SAS}}
& \multicolumn{2}{c}{  \rotatebox{80}{HyperTensioN}}
& \multicolumn{2}{c}{  \rotatebox{80}{Lilotane}} \\ 
			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}  \cmidrule(lr){13-14} \cmidrule(lr){15-16}    
			& &PO & TO & PO & TO & PO & TO & PO & TO   \\ 
			\midrule 
			Barman-BDI  \\ 
			Monroe Fully Observ. \\ 
			Monroe Part. Observ. \\ 
			PCP\\ 
			Rover  \\ 
			Satellite  \\ 
			Transport \\ 
			UM-Translog \\ 
			Woodworking \\ 
			\midrule 
			Monroe  \\ 
			SmartPhone \\ 
			Zenotravel \\ 
			\midrule 
			IPC \\
			\bottomrule
		\end{tabular} 	
	}
\end{table*}
